### 2025-05-13 Chapters/resources.tex
changes

>>>>

\section{published and submitted work }

\begin{itemize}
		\item \textit{Automated Sleep Staging System Using EEG Signal Feature-Based Classification by Machine Learning Techniques}, Tanmay Rathod, Santosh Kumar Satapathy, Nibedita Das, Rajesh Kumar Mohapatra, Suren Kumar Sahu, Vaishvi R Shah, 2024 IEEE 8th International Conference on Information and Communication Technology (CICT). \url{https://ieeexplore.ieee.org/document/10899578}

	\item \textit{Automated Sleep Staging System with EEG Signal using Machine Learning Techniques}, Santosh Kumar Satapathy, Tanmay Rathod, Nibedita Das, Rajesh Kumar Mohapatra, Suren Sahu, Jaynil Joshi, 2025 IEEE International Conference on Interdisciplinary Approaches in Technology and Management for Social Innovation (IATMSI). \url{https://ieeexplore.ieee.org/document/10985276}

	  \item \textit{SleepGCN-Transformer: A Hybrid Graph-Convolutional Approach for EEG-based Sleep Staging}, Tanmay Rathod et al., submitted to \textit{Biomedical Signal Processing and Control}, May 2025 (under review).

	\end{itemize}

\section{Contact Information}

For inquiries or collaboration, contact the author via the following:

\begin{itemize}
	\item \textbf{Email:} \href{mailto:tanmayrathod777@gmail.com}{tanmayrathod777@gmail.com}
	\item \textbf{GitHub:} \url{https://github.com/tanmay007thor}
	\item \textbf{IEEE Xplore Author Profile:} \url{https://ieeexplore.ieee.org/author/577823064896395}
	\item \textbf{Portfolio Website:} \url{https://tanmay-dev.netlify.app/}
	\item \textbf{LinkedIn:} \url{https://www.linkedin.com/in/tanmay-rathod-15a332230}
	\item \textbf{Phone:} +91 90165 89777
\end{itemize}
